Indirect climate effects on biomass partitioning

### 2014-11-19 manuscript/draftpaper.Rnw
Climate space figure now removes areas without woody vegetation

@@

\begin{figure}[h!]
    \centering
    \includegraphics{Figure1_MAPMAT_baad_vs_worldclim.pdf}
    \caption{Global coverage of the climate space by the dataset. Hexagons are terrestrial observations extracted from Worldclim (colored by number of 0.5\degree~cells, cut off at 6000mm MAP). Note that Worldclim observations include land areas where woody vegetation does not occur (e.g., desert, tundra). Triangles are averages for the three PFTs across all contributed studies. }
    \label{fig:figure1}
\end{figure}

>>>>

Moisture index and growing season temperature were taken from Lin et al. (in review).

@@

\begin{figure}[h!]
    \centering
    \includegraphics{Figure1_MAPMAT_baad_vs_worldclim.pdf}
    \caption{Global coverage of the climate space by the dataset. Hexagons are terrestrial observations extracted from Worldclim \cite{worldclim} (colored by number of 0.5\degree~cells, cut off at 6000mm MAP), excluding areas without woody vegetation (taken from the global land cover database GLC-SHARE \cite{lathamglobal}) Triangles are averages for the three PFTs across all contributed studies. }
    \label{fig:figure1}
\end{figure}
